---
title: "SVM Prediction"
author: Peyman Farshidfar, Gerit Imhoff, Pia Fragge, Volker Paatz
output: html_notebook
---

```{r}
# Importing Function Packages
source("prep_environment.R")
# Importing Datenaufbereitung
source("prep_data.R")

```


## Splitting Training and Test Data

```{r}
# Setting the random counter to a fixed value, so the random initialization stays the same (the random split is always the same)
set.seed(1)
# Shuffling the dataset (to get random orders within each dataset as well)
new_row_order <- sample(nrow(fullData_dummy))
fullData_dummy <- fullData_dummy[new_row_order,]
# Assign each row number in the full dataset randomly to one of the three groups of datasets
# The probability of being in one of the groups results then in crresponding group sizes
assignment <- sample(1:2, size = nrow(fullData_dummy), prob = c(.9, .1), replace = TRUE)
# Create training and test datasets
train_dataset <- fullData_dummy[assignment == 1, ]  # subset house_pricing to training indices only
test_dataset <- fullData_dummy[assignment == 2, ]  # subset house_pricing to test indices only
```


## Data Preparation

```{r}
# Uncomment the next line if you want to check the correctness of your following code for the svm estimation with a small (and computationally fast) part of the training data set
train_dataset <- sample_frac(train_dataset, .10)
```


## Training the SVM
```{r}
colnames(fullData_dummy)
```

```{r echo=FALSE}
# Optimization of an SVM with standard hyper parameters
# Durch die dummy Variablen sind es viele Variablen.
model_svm <- svm(Umsatz ~ 
                   Warengruppe_Brot +Warengruppe_Broetchen +Warengruppe_Crossaint +Warengruppe_Konditorei + Warengruppe_Kuchen +
                   Monat_1 + Monat_2 + Monat_3 + Monat_4 + Monat_5 + Monat_6 + Monat_7 + Monat_8 + Monat_9 + Monat_10 + Monat_11 +
                   Wochentag_Montag + Wochentag_Dienstag + Wochentag_Mittwoch + Wochentag_Donnerstag + Wochentag_Freitag + Wochentag_Samstag + Ferien + Feiertag + Wochenende  + Umsatz_naiv + Umsatz_mean + KielerWoche + Temperatur_1 + Temperatur_2 + Temperatur_3 + Temperatur_4 + Temperatur_5 + Sonnenscheindauer, train_dataset)
```

SVM with hyper paramter tuning via grid search and cross validation

```{r}
svm_tune <- tune(svm, Umsatz ~ Warengruppe_Brot +Warengruppe_Broetchen +Warengruppe_Crossaint +Warengruppe_Konditorei + Warengruppe_Kuchen +
                   Monat_1 + Monat_2 + Monat_3 + Monat_4 + Monat_5 + Monat_6 + Monat_7 + Monat_8 + Monat_9 + Monat_10 + Monat_11 +
                   Wochentag_Montag + Wochentag_Dienstag + Wochentag_Mittwoch + Wochentag_Donnerstag + Wochentag_Freitag + Wochentag_Samstag + Ferien + Feiertag + Wochenende  + Umsatz_naiv + Umsatz_mean + KielerWoche + Temperatur_1 + Temperatur_2 + Temperatur_3 + Temperatur_4 + Temperatur_5 + Sonnenscheindauer, data=train_dataset, ranges = list(epsilon = 0.08, cost =1.5)) #seq(0.05,0.3,0.05), cost = seq(1,4,0.5)

##Auskommentieren, wenn Modell gespeichert werden soll.
#saveRDS(svm_tune, "svm_tune1.rds")
#readRDS("svm_tune1.rds") Umsatz_naiv + Umsatz_mean

svm_tune$best.model
```


## Checking the Prediction Quality


### Trainig Data

<!-- SVM with a standard hyperparameters -->
```{r echo=FALSE}
# Calculating the prediction for the training data using the best model according to the grid search
pred_train <- predict(model_svm, train_dataset)
# Calculating the prediction quality for the training data using the MAPE
mape(train_dataset$Umsatz, pred_train)
```
<!--Grafische Darstellung der Ergebnisse -->
```{r echo=FALSE}
# Bargraph der mittleren Umsatzdaten nach Wochentag pro Warengruppe
train_dataset$pred <- pred_train

ggplot(train_dataset)+
  geom_line( aes(x =Datum, y = Umsatz, colour="skyblue"), stat="summary", fun="mean")+
  geom_line( aes(x =Datum, y = pred, colour="orange"), stat="summary", fun="mean")+
  xlab("Datum") + ylab("Umsatz") +
  facet_wrap(~Warengruppe , scales="free")+
  scale_color_discrete(name = "Umsatz", labels = c("vorhergesagt", "tatsächlich"))
```

SVM with hyperparameters tuned via grid search and cross validation
```{r}
# Calculating the prediction for the training data using the best model according to the grid search
pred_train <- predict(svm_tune$best.model, train_dataset)
# Calculating the prediction quality for the training data using the MAPE
mape(train_dataset$Umsatz, pred_train)
```
Grafische Darstellung der Ergebnisse
```{r}
# Bargraph der mittleren Umsatzdaten nach Wochentag pro Warengruppe
train_dataset$pred <- pred_train

ggplot(train_dataset)+
  geom_line( aes(x =Datum, y = Umsatz, colour="skyblue"), stat="summary", fun="mean")+
  geom_line( aes(x =Datum, y = pred, colour="orange"), stat="summary", fun="mean")+
  xlab("Datum") + ylab("Umsatz") +
  facet_wrap(~Warengruppe , scales="free")+
  scale_color_discrete(name = "Umsatz", labels = c("vorhergesagt", "tatsächlich"))
```

### Test Data

<!--SVM with a standard hyperparameters -->
```{r echo=FALSE}
# Calculating the prediction for the validation data using the best model according to the grid search
pred_test <- predict(model_svm, test_dataset)
# Calculating the prediction quality for the validation data using the MAPE
mape(test_dataset$Umsatz, pred_test)
```
<!--Grafische Darstellung der Ergebnisse -->
```{r echo=FALSE}
# Bargraph der mittleren Umsatzdaten nach Wochentag pro Warengruppe
test_dataset$pred <- pred_test

ggplot(test_dataset)+
  geom_line( aes(x =Datum, y = Umsatz, colour="skyblue"), stat="summary", fun="mean")+
  geom_line( aes(x =Datum, y = pred, colour="orange"), stat="summary", fun="mean")+
  xlab("Datum") + ylab("Umsatz") +
  facet_wrap(~Warengruppe , scales="free")+
  scale_color_discrete(name = "Umsatz", labels = c("vorhergesagt", "tatsächlich"))
```

SVM with hyperparameters tuned via grid search and cross validation
```{r}
# Calculating the prediction for the test data using the best model according to the grid search
pred_test <- predict(svm_tune$best.model, test_dataset)
# Calculating the prediction quality for the test data using the MAPE
mape(test_dataset$Umsatz, pred_test)
```
Grafische Darstellung der Ergebnisse
```{r}
# Bargraph der mittleren Umsatzdaten nach Wochentag pro Warengruppe
test_dataset$pred <- pred_test

ggplot(test_dataset)+
  geom_line( aes(x =Datum, y = Umsatz, colour="skyblue"), stat="summary", fun="mean")+
  geom_line( aes(x =Datum, y = pred, colour="orange"), stat="summary", fun="mean")+
  xlab("Datum") + ylab("Umsatz") +
  facet_wrap(~Warengruppe , scales="free")+
  scale_color_discrete(name = "Umsatz", labels = c("vorhergesagt", "tatsächlich"))
```

### New Data

SVM with a standard hyperparameters
```{r}
# Calculating the prediction for the new data (next day) using the best model according to the grid search
Umsatz_predicted <- predict(svm_tune$best.model, newData)
prediction <- data.frame(Umsatz_predicted)
prediction$Warengruppe <- newData$Warengruppe
prediction$Datum <- newData$Datum
prediction$Monat <- newData$Monat

unlink("svm_prediction_1.csv")
    writecsvData <- prediction
    writecsvData <- cbind(ID = 1:nrow(writecsvData), writecsvData)

    write.csv(writecsvData,"svm_prediction_1.csv", append = FALSE, quote = TRUE, sep = ",",
              eol = "\n", na = "NA", dec = ".", row.names = FALSE,
              col.names = TRUE, qmethod = c("escape", "double"),
              fileEncoding = "")

prediction
```
```{r}

ggplot(prediction) +
  geom_bar( aes(x=Warengruppe, y=Umsatz_predicted), stat="identity", fill="forestgreen", alpha=0.5)
```



```{r}
##Da das Saisonbrot nur im Oktober, November oder Dezember verkauft wird, überprüfen, ob sich Vorhersagedatum in dem Zeitraum befindet, ansonsten Umsatz_predicted = 0 setzen
for (i in 1:nrow(prediction)){
  if ((!(prediction$Monat[i]==10 | prediction$Monat[i]==11 | prediction$Monat[i]==12)) & prediction$Warengruppe[i]=="Saisonbrot") {
    prediction$Umsatz_predicted[i] <- 0
  }
}
    
unlink("svm_prediction_2.csv")
    writecsvData <- prediction
    writecsvData <- cbind(ID = 1:nrow(writecsvData), writecsvData)

    write.csv(writecsvData,"svm_prediction_2.csv", append = FALSE, quote = TRUE, sep = ",",
              eol = "\n", na = "NA", dec = ".", row.names = FALSE,
              col.names = TRUE, qmethod = c("escape", "double"),
              fileEncoding = "")    

prediction
```


```{r}

ggplot(prediction) +
  geom_bar( aes(x=Warengruppe, y=Umsatz_predicted), stat="identity", fill="forestgreen", alpha=0.5)
```

